FTLR proof cases

### 2018-05-24 fully-abstract-comp/ftlr-proof-cases.tex
Corrected name of downwards closure lemma

\subsection{Lemmas}
In this section, I have listed lemmas that seem to be necessary for the FTLR proof.
\begin{lemma}[non-expansiveness of relations]
  \label{lem:non-expansive}
  If $n' \leq n$, then
  \begin{itemize}
  \item If $\npair{(b,e)} \in \readCond{\lin,W}$, then $\npair[n']{(b,e)} \in \readCond{\lin,W}$.
  \item $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W}$, then also $\memSat[n']{(\ms_S,\stk,\ms_\stk,\ms_T)}{W}$.
  \end{itemize}
\end{lemma}

@@

  It remains to prove that $\memSat[n']{(\ms_S\update{\aaddr}{w_S},\stk,\ms_\stk,\ms_T\update{\aaddr'}{w_T})}{W_M'}$.
  We have to distinguish the case that $\isLinear{\ms_S(\aaddr)}$ and the opposite case.
  \begin{itemize}
  \item case $\isLinear{\ms_S(\aaddr)}$: then $\linCons{\ms_S(\aaddr)} = 0$ and it follows from $\npair[n']{(\ms_S(\aaddr),\ms_T(\aaddr'))}\in\lrv(H_\sigma,W)$ that also $\isLinear{\ms_T(\aaddr')}$ \dominique{Do we need a lemma for this?} and $\linCons{\ms_T(\aaddr')} = 0$. 
    From $\linConsPerm{\perm}{\ms_S(\aaddr)}$ and $\linConsPerm{\perm'}{\ms_T(\aaddr')}$, we then also get that $\perm,\perm' \in \writeAllowed{}$ and from $\npair{(c,c')}\in\lrv(H_\sigma,W)$, it then follows that $\npair{(\baddr,eaddr)} \in \writeCond{\lin,W}$.
    From the ``Additionally, if..'' case in Lemma~\ref{lem:readcond-writecond-work} with Lemma~\ref{lem:non-expansive}, we then get that $\memSat[n']{(\ms_S\update{\aaddr}{w_S},\stk,\ms_\stk,\ms_T\update{\aaddr'}{w_T})}{W_M'}$.

  \item case $\neg\isLinear{\ms_S(\aaddr)}$: then $\linCons{\ms_S(\aaddr)} = \ms_S(\aaddr)$ and it follows from $\npair[n']{(\ms_S(\aaddr),\ms_T(\aaddr'))}\in\lrv(H_\sigma,W)$ that also $\neg\isLinear{\ms_T(\aaddr')}$ \dominique{Do we need a lemma for this?} and $\linCons{\ms_T(\aaddr')} = \ms_T(\aaddr')$.
    The fact that $\memSat[n']{(\ms_S\update{\aaddr}{w_S},\stk,\ms_\stk,\ms_T\update{\aaddr'}{w_T})}{W_M'}$ then follows simply by non-expansiveness of memory satisfaction, i.e. Lemma~\ref{lem:non-expansive}.
  \end{itemize}
\end{proof}

@@

  It remains to prove that $\memSat{(\ms_S,\stk,\ms_\stk\update{\aaddr}{w_S},\ms_T\update{\aaddr'}{w_T})}{W_M'}$.
  We have to distinguish the case that $\isLinear{\ms_\stk(\aaddr)}$ and the opposite case.
  \begin{itemize}
  \item case $\isLinear{\ms_\stk(\aaddr)}$: then $\linCons{\ms_\stk(\aaddr)} = 0$ and it follows from $\npair[n']{(\ms_\stk(a),\ms_T(a))}\in\lrv(H_\sigma,W)$ that also $\isLinear{\ms_T(\aaddr')}$ \dominique{Do we need a lemma for this?} and $\linCons{\ms_T(\aaddr')} = 0$. 
    From $\linConsPerm{\perm}{\ms_S(\aaddr)}$ and $\linConsPerm{\perm'}{\ms_T(\aaddr')}$, we then also get that $\perm = \perm' \in \writeAllowed{}$ and from $\npair{(c,c')}\in\lrvg{\trust}(H_\sigma,W)$, it then follows that $\npair{(\baddr,eaddr)} \in \stackWriteCond{W}$.
    From the ``Additionally, if..'' case in Lemma~\ref{lem:readcond-writecond-work} with Lemma~\ref{lem:non-expansive}, we then get that $\memSat[n']{(\ms_S,\stk,\ms_\stk\update{\aaddr}{0},\ms_T\update{\aaddr'}{0})}{W_M'}$.

  \item case $\neg\isLinear{\ms_\stk(\aaddr)}$: then $\linCons{\ms_\stk(\aaddr)} = \ms_\stk(\aaddr)$ and it follows from $\npair[n']{(\ms_\stk(a),\ms_T(a))}\in\lrv(H_\sigma,W)$ that also $\neg\isLinear{\ms_T(\aaddr')}$ \dominique{Do we need a lemma for this?} and $\linCons{\ms_T(\aaddr')} = \ms_T(\aaddr')$.
    The fact that $\memSat[n']{(\ms_S\update{\aaddr}{w_S},\stk,\ms_\stk,\ms_T\update{\aaddr'}{w_T})}{W_M'}$ then follows simply by non-expansiveness of memory satisfaction, i.e. Lemma~\ref{lem:non-expansive}.
  \end{itemize}
\end{proof}

@@

and pick
\item $\Phi_S' = \Phi_S\updReg{\pcreg}{c}$
\item $\Phi_T' = \Phi_T\updReg{\pcreg}{c}$

@@

    \item (cca,seta2b) $w_1 = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma,\sigma'}$, $w_1' = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma,\sigma'}$, $\Phi_S(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma,\sigma'}$ and $\Phi_T(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma,\sigma'}$, $k = 1$

>>>>

\subsection{Lemmas}
In this section, I have listed lemmas that seem to be necessary for the FTLR proof.
\begin{lemma}[Downwards closure of relations]
  \label{lem:downwards-closed}
  If $n' \leq n$, then
  \begin{itemize}
  \item If $\npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}$, then $\npair[n']{(\baddr,\eaddr)} \in \xReadCond{\lin,W}$.
  \item If $\npair{(\baddr,\eaddr)} \in \readCond{\lin,W}$, then $\npair[n']{(\baddr,\eaddr)} \in \readCond{\lin,W}$.
  \item $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W}$, then also $\memSat[n']{(\ms_S,\stk,\ms_\stk,\ms_T)}{W}$.
  \item If $\npair{(\reg_S,\reg_T)} \in \lrr(W)$, then $\npair[n']{(\reg_S,\reg_T)} \in \lrr(W)$.
  \end{itemize}
\end{lemma}

\begin{lemma}[Non-expansiveness of relations]
  \label{lem:non-expansiveness}
  If $W \nequal W'$, then
  \begin{itemize}
  \item $\npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W} \nequal \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W'}$.
  \item ...
  \end{itemize}
\end{lemma}

@@

  It remains to prove that $\memSat[n']{(\ms_S\update{\aaddr}{w_S},\stk,\ms_\stk,\ms_T\update{\aaddr'}{w_T})}{W_M'}$.
  We have to distinguish the case that $\isLinear{\ms_S(\aaddr)}$ and the opposite case.
  \begin{itemize}
  \item case $\isLinear{\ms_S(\aaddr)}$: then $\linCons{\ms_S(\aaddr)} = 0$ and it follows from $\npair[n']{(\ms_S(\aaddr),\ms_T(\aaddr'))}\in\lrv(H_\sigma,W)$ that also $\isLinear{\ms_T(\aaddr')}$ \dominique{Do we need a lemma for this?} and $\linCons{\ms_T(\aaddr')} = 0$. 
    From $\linConsPerm{\perm}{\ms_S(\aaddr)}$ and $\linConsPerm{\perm'}{\ms_T(\aaddr')}$, we then also get that $\perm,\perm' \in \writeAllowed{}$ and from $\npair{(c,c')}\in\lrv(H_\sigma,W)$, it then follows that $\npair{(\baddr,eaddr)} \in \writeCond{\lin,W}$.
    From the ``Additionally, if..'' case in Lemma~\ref{lem:readcond-writecond-work} with Lemma~\ref{lem:downwards-closed}, we then get that $\memSat[n']{(\ms_S\update{\aaddr}{w_S},\stk,\ms_\stk,\ms_T\update{\aaddr'}{w_T})}{W_M'}$.

  \item case $\neg\isLinear{\ms_S(\aaddr)}$: then $\linCons{\ms_S(\aaddr)} = \ms_S(\aaddr)$ and it follows from $\npair[n']{(\ms_S(\aaddr),\ms_T(\aaddr'))}\in\lrv(H_\sigma,W)$ that also $\neg\isLinear{\ms_T(\aaddr')}$ \dominique{Do we need a lemma for this?}
    and $\linCons{\ms_T(\aaddr')} = \ms_T(\aaddr')$.
    The fact that $\memSat[n']{(\ms_S\update{\aaddr}{w_S},\stk,\ms_\stk,\ms_T\update{\aaddr'}{w_T})}{W_M'}$ then follows simply by downwards closure of memory satisfaction, i.e.~Lemma~\ref{lem:downwards-closed}.
  \end{itemize}
\end{proof}

@@

  It remains to prove that $\memSat{(\ms_S,\stk,\ms_\stk\update{\aaddr}{w_S},\ms_T\update{\aaddr'}{w_T})}{W_M'}$.
  We have to distinguish the case that $\isLinear{\ms_\stk(\aaddr)}$ and the opposite case.
  \begin{itemize}
  \item case $\isLinear{\ms_\stk(\aaddr)}$: then $\linCons{\ms_\stk(\aaddr)} = 0$ and it follows from $\npair[n']{(\ms_\stk(a),\ms_T(a))}\in\lrv(H_\sigma,W)$ that also $\isLinear{\ms_T(\aaddr')}$ \dominique{Do we need a lemma for this?} and $\linCons{\ms_T(\aaddr')} = 0$. 
    From $\linConsPerm{\perm}{\ms_S(\aaddr)}$ and $\linConsPerm{\perm'}{\ms_T(\aaddr')}$, we then also get that $\perm = \perm' \in \writeAllowed{}$ and from $\npair{(c,c')}\in\lrvg{\trust}(H_\sigma,W)$, it then follows that $\npair{(\baddr,eaddr)} \in \stackWriteCond{W}$.
    From the ``Additionally, if..'' case in Lemma~\ref{lem:readcond-writecond-work} with Lemma~\ref{lem:downwards-closed}, we then get that $\memSat[n']{(\ms_S,\stk,\ms_\stk\update{\aaddr}{0},\ms_T\update{\aaddr'}{0})}{W_M'}$.

  \item case $\neg\isLinear{\ms_\stk(\aaddr)}$: then $\linCons{\ms_\stk(\aaddr)} = \ms_\stk(\aaddr)$ and it follows from $\npair[n']{(\ms_\stk(a),\ms_T(a))}\in\lrv(H_\sigma,W)$ that also $\neg\isLinear{\ms_T(\aaddr')}$ \dominique{Do we need a lemma for this?}
    and $\linCons{\ms_T(\aaddr')} = \ms_T(\aaddr')$.
    The fact that $\memSat[n']{(\ms_S\update{\aaddr}{w_S},\stk,\ms_\stk,\ms_T\update{\aaddr'}{w_T})}{W_M'}$ then follows simply by downwards closure of memory satisfaction, i.e.\ Lemma~\ref{lem:downwards-closed}.
  \end{itemize}
\end{proof}

@@

@@

    \item (cca,seta2b) $w_1 = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma'}$, $w_1' = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma'}$, $\Phi_S(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma'}$ and $\Phi_T(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma'}$, $k = 1$
